An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-09-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
suggestion for a lollipop visual

>>>>

p.seg_252_plot <- table.252.cmps_seg %>%
  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
               names_to = "Metric") %>%
  ggplot(aes(x = factor(seg_length))) +
  geom_bar(aes(weight =  value, fill = Metric), position=position_dodge(width = 0.5), width=.1) +
  geom_point(aes(y =  value, color = Metric), position=position_dodge(width = 0.5), size = 5) +
#  scale_x_continuous(breaks = table.252.cmps_seg$seg_length) +
  theme_bw() +
  ggtitle("A Temp Title") +
  ylab("Sum of Squares Ratio") + 
  xlab("seg_length")
